MaxEnt: What is it good for?

### 2015-06-21 ms.tex
notation

\section{Special case 1: expected values}\label{sec:expectations}
The most common kind of testable information analysed using MaxEnt is
expected values.

 Updating from a prior $\boldsymbol{q}$ to a posterior
$\boldsymbol{p}$ given an expected value constraint:

\begin{eqnarray}
\left<f(x)\right>_{\boldsymbol{p}} = \sum_{i=1}^N p_i f(x_i) = F.
\end{eqnarray}

>>>>

\section{Special case 1: expected values}\label{sec:expectations}
The most common kind of testable information analysed using MaxEnt is
expected values. An expected value is a property of a probability distribution,
and we can imagine updating from a prior $q$ to a posterior
$p$ when we receive information that specifies an expected value.
For example, suppose we apply the constraint (the testable information)
that the expected value of $f(x)$ should equal some known value $F$. That is:
\begin{eqnarray}
\left<f(x)\right>_p = \sum_x p(x)f(x) = F.
\end{eqnarray}
